---
title: "donations project"
author: "saheed"
date: "2022-12-01"
output: html_document
---

```{r}
library(dplyr)
library(tidyverse)
library(data.table)
library(ggplot2)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
 - How many donors we have in existing database? 
 
```{r}
dd<-donation_data_nw
drd<-donor_data_new
dim(dd)
dim(drd)
```

 COUNT OF MALE DONOR
```{r}
sum(with(dd,gender == "Male"))


```
COUNT OF FEMALE DORNO
```{r}
sum(with(dd,gender == "Female"))

```
COUNT OF ALL DONOR
```{r}
length(dd$last_name)
```
Total donations
```{r}
  sum(dd$donations
      )
```
Total donation by each gender
```{r}
DBYEACHG <- dd %>% 
 group_by(gender) %>% 
 summarise( Total_donation_by_each_gender
= sum(donations))

```
Total amount donated by each job field
```{r}
total_job_field <- 
dd%>%
  group_by(job_field)%>%
  summarise(donation_by_each_job_field= sum(donations)
) %>%
  arrange(desc(donation_by_each_job_field))
```


ggrepel.... was used

```{r}
library(ggrepel)

pie <- ggplot(total_job_field, aes( x= "", y ="donation_by_each_job_field", fill = job_field))+
  geom_col(color ='black')+
  coord_polar("y", start = 0)+
  geom_text(aes(label = paste0(round(donation_by_each_job_field*100), "%")), 
         position = position_stack(vjust =0.5))+
 # theme(legend.position = "none")+
  theme(panel.background = element_blank(),
        axis.line = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
  plot.title = element_text(hjust = 0.5, size = 18))+
  ggtitle("Job firld donations(ggplot2)")+
  #geom_label_repel(aes(label = donation_by_each_job_field), size=2, show.legend = F, nudge_x = 4, box.padding = 0.25, label.padding = 0.25) +
       scale_fill_manual(values = colors)
       
pie
```




```{r}
pie<-ggplot(total_job_field) +
  aes(
    x = job_field,
    y = donation_by_each_job_field,
    fill = job_field
  ) +
  geom_col() +
  scale_fill_manual(
    values = c(Accounting = "#F8766D",
    `Business Development` = "#DD8A1D",
    Engineering = "#B59C00",
    `Human Resources` = "#78AC0A",
    Legal = "#0DB832",
    Marketing = "#00BE79",
    `Product Management` = "#00BEB7",
    `Research and Development` = "#08B6E5",
    Sales = "#4FA1F9",
    Services = "#A385FC",
    Support = "#E46DEB",
    Training = "#FF61C3")
  ) +
  theme_minimal()
pie
  
```







AMOUNT DONATED BY EACH GENDER AND THEIR  JOB FIELD

```{r}
gender_job_field_donations <-dd%>%
  group_by(job_field,gender)%>%
  summarise(donation_by_each_job_field= sum(donations)
) %>%
  arrange(desc(job_field))
```
TOP 10 DORNOR

```{r}
TOP10<-
dd%>%
  arrange(desc(donations))%>%
  slice(1:10)
```
LOWEST 10 DORNO


```{r}
dd%>%
  arrange(donations)%>%
  slice(1:10)
```
TOP 10 MALE and FEMALE DORNO
```{r}
TOP10_MALE_and_FEMALE_DORN<-
dd%>%
  arrange(desc(donations))%>%
  group_by(gender)%>%
  slice(1:10)
```

SUM OF DONATION FROM EACH STATE
```{r}
dd%>%
  group_by(state)%>%
  summarise(donation_by_each_job_field= sum(donations)
) %>%
  arrange(desc(donation_by_each_job_field))
```
TOP 10 STATE WITH HIGEST DORNO
```{r}
#state_donor=
dd%>%
  group_by(state)%>%
  summarise(state_donation= sum(donations)
) %>%
  arrange(desc(state_donation))%>%
  slice(1:10)
```

```{r}

 dd%>%
  group_by(state,gender)%>%
  summarise(state_donation= sum(donations)
) %>%
  arrange(desc(state_donation))%>%
  slice(1:10)
```

```{r}
library(openxlsx)
library(rio)
export(state_donation, 'state_donations.xlsx')

```

```{r}
export(state_donation, 'state_donations.xlsx')

```


AVERAGE DONATIONS FROM EACH GENDER
```{r}
dd%>%
  group_by(gender)%>%
  summarise(average_donation = mean(donations))
```
To find sum and count of donation from all state , I used  SUM, COUNT, WHERE, GROUP BY, AS:



```{r}
count_and_total_donation_country<-dd%>%
  group_by(state)%>%
  summarise(count = n_distinct(donations),sum(donations))%>%
  arrange(desc(count))

```

To find sum and count of donation from all state , I used  SUM, COUNT, WHERE, GROUP BY, AS:


```{r}
count_and_total_donation_jobfield<-dd%>%
  group_by(job_field)%>%
  summarise(count = n_distinct(donations),sum_donation =sum(donations))%>%
  arrange(desc(sum_donation))

```

The count of donor from each job field and sum of donation by donation frequeency


```{r}
donorinerj <-inner_join(dd, drd, by = "id")

view(donorinerj)
dim(donorinerj)
```

SUM OF DONATION IN EACH DEPARTMENT BY DONATION FREQUENCIES
```{r}
donorinerj%>%
  group_by(job_field, donation_frequency)%>%
  summarise(count = n_distinct(donations),sum_donation =sum(donations))#%>%
  #arrange(desc(sum_donation))

```
List of female donor that donate above 450 without university

```{r}
donorinerj%>%
  select(gender, donations, university)%>%
  filter( gender == 'Female',donations >450, university == 'null')%>%
  arrange(desc(donations))
```
Top 10 university dorno

```{r}
Top10_university_dorno <-
donorinerj%>%
  select( fisst_name, last_name,gender,donations,donation_frequency,job_field, university)%>%
  arrange(desc(donations))%>%
  slice(1:10)
```



List of male donor that donate above 450 without university

```{r}
donorinerj%>%
  select(gender, donations, university)%>%
  filter( gender == 'Male',donations >450, university == 'null')%>%
  arrange(desc(donations))

```


COUNT OF MALE DONOR FROM EACH DEPARTMENT
```{r}
#male_count<-
donorinerj%>%
  group_by(job_field, gender)%>%
  summarise(count = n_distinct(donations))%>%
  filter(gender == 'Male')%>%
  arrange(desc(count))
```



```{r}
male_count$job_field <- factor(male_count$job_field)%>%
  fct_reorder(male_count$count)


ggplot(male_count) +
  aes(x = job_field, y = count, fill = job_field) +
  geom_col() +
  scale_fill_hue(direction = 1) +
  coord_flip() +
  theme_minimal() +
  theme(legend.position = "none")+
    geom_text(aes(label = signif(count)), nudge_y = 1, color = 'blue', size = 2)

```

COUNT OF FEMALE DONOR FROM EACH DEPARTMENT
```{r}
female_count$job_field <- factor(female_count$job_field)%>%
  fct_reorder(female_count$count)


#female_count<-
donorinerj%>%
  group_by(job_field, gender)%>%
  summarise(count = n_distinct(donations))%>%
  filter(gender == 'Female')%>%
  arrange(desc(count))
```


```{r}

female_count$job_field <- factor(female_count$job_field)%>%
  fct_reorder(female_count$count)

ggplot(female_count) +
  aes(x = job_field, y = count, fill = job_field) +
  geom_col() +
  scale_fill_manual(
    values = c(Accounting = "#F8766D",
    `Business Development` = "#DD8A1D",
    Engineering = "#B59C00",
    `Human Resources` = "#78AC0A",
    Legal = "#0DB832",
    Marketing = "#00BE79",
    `Product Management` = "#00BEB7",
    `Research and Development` = "#08B6E5",
    Sales = "#4FA1F9",
    Services = "#A385FC",
    Support = "#E46DEB",
    Training = "#FF61C3")
  ) +
  coord_flip() +
  theme_minimal() +
  theme(legend.position = "none")+
   geom_text(aes(label = signif(count)), nudge_y = 1, color = 'blue', size = 2)

```





FEMALE WITHOUT CAR AND UNIVERSITY THAT DONATED MORE THAN $400
```{r}
female_without_car_and_uni <-donorinerj%>%
  select(fisst_name, last_name, state, job_field,gender, donations,donation_frequency, university,cars)%>%
  filter( gender == 'Female',donations >450, university == 'null',cars=='null')%>%
  arrange(desc(donations))
```

FEMALE WITHOUT CAR AND UNIVERSITY THAT DONATED MORE THAN $400
```{r}
male_without_car_and_uni<-donorinerj%>%
  select(fisst_name, last_name, state, job_field,gender, donations,donation_frequency, university,cars)%>%
  filter( gender == 'Male',donations >450, university == 'null',cars=='null')%>%
  arrange(desc(donations))

```

4 MALE DORNO WITHOUT CARS
```{r}
donorinerj%>%
  select(gender, donations,cars)%>%
  filter( gender == 'Male',donations >450,cars=='null')%>%
  arrange(desc(donations))
```
FEMALE DORNO WITHOUT CARS

```{r}
donorinerj%>%
  select(last_name ,fisst_name,gender, donations,cars,email )%>%
  filter( gender == 'Female',cars=='null')%>%
  arrange(desc(donations))

```


```{r}
leftjoin <- left_join(dd, drd, by = "id")

```

MALE DORNO WITHOUT CARS

```{r}
donorinerj%>%
  select(gender, donations,cars)%>%
  filter( gender == 'Male',cars=='null')%>%
  arrange(desc(donations))
```
THE SUM OF DONATIONS MADE ONCE BY FEMALE IN RELATED TO THEIR
JOBS
```{r}
donorinerj%>%
  select(gender, donations,donation_frequency,job_field)%>%
  filter( gender == 'Male', donation_frequency == 'Once')%>%
  summarise(sum_donation = sum(donations))
```
FEMALE
```{r}
donorinerj%>%
  select(gender, donations,donation_frequency,job_field)%>%
  filter( gender == 'Female', donation_frequency == 'Once')%>%
  summarise(sum_donation = sum(donations))
```

sum Male/Weekly

```{r}
donorinerj%>%
  select(gender, donations,donation_frequency,job_field)%>%
  filter( gender == 'Male', donation_frequency == 'Weekly')%>%
  summarise(sum_donation = sum(donations))
```
sum Female/weekly
```{r}
donorinerj%>%
  select(gender, donations,donation_frequency,job_field)%>%
  filter( gender == 'Female', donation_frequency == 'Weekly')%>%
  summarise(sum_donation = sum(donations))
```
sum Male/monthly
```{r}
donorinerj%>%
  select(gender, donations,donation_frequency,job_field)%>%
  filter( gender == 'Male', donation_frequency == 'Monthly')%>%
  summarise(sum_donation = sum(donations))
```
Sum Female/Monthly
```{r}
donorinerj%>%
  select(gender, donations,donation_frequency,job_field)%>%
  filter( gender == 'Female', donation_frequency == 'Monthly')%>%
  summarise(sum_donation = sum(donations))
```

Sum Male/Yearly
```{r}
donorinerj%>%
  select(gender, donations,donation_frequency,job_field)%>%
  filter( gender == 'Male', donation_frequency == 'Yearly')%>%
  summarise(sum_donation = sum(donations))
```

sum Female/Yearly
```{r}
donorinerj%>%
  select(gender, donations,donation_frequency,job_field)%>%
  filter( gender == 'Female', donation_frequency == 'Yearly')%>%
  summarise(sum_donation = sum(donations))
```

THE SUM OF DONATIONS MADE YEAR BY FEMALE IN EACH STATE IN RELATED TO THEIR
JOBS

```{r}
donorinerj%>%
  group_by(state, donation_frequency,gender, job_field)%>%
  filter(donation_frequency=='Yearly', gender=='Female')%>%
  summarise(count = n_distinct(donations),sum_donation =sum(donations))%>%
  arrange(desc(sum_donation))
```
THE SUM OF DONATIONS MADE YEAR BY FEMALE IN EACH STATE IN RELATED TO THEIR
JOBS
```{r}
donorinerj%>%
  group_by(state, donation_frequency,gender, job_field)%>%
  filter(donation_frequency=='Yearly', gender=='Male')%>%
  summarise(count = n_distinct(donations),sum_donation =sum(donations))%>%
  arrange(desc(sum_donation))
```
THE SUM OF DONATIONS MADE YEAR BY FEMALE IN EACH STATE IN RELATED TO THEIR
JOBS

```{r}
donorinerj%>%
  group_by(state, donation_frequency,gender, job_field)%>%
  filter(donation_frequency=='Monthly', gender=='Female')%>%
  summarise(count = n_distinct(donations),sum_donation =sum(donations))%>%
  arrange(desc(sum_donation))


```

MALE/MONTHLY
```{r}
donorinerj%>%
  group_by(state, donation_frequency,gender, job_field)%>%
  filter(donation_frequency=='Monthly', gender=='Male')%>%
  summarise(count = n_distinct(donations),sum_donation =sum(donations))%>%
  arrange(desc(sum_donation))


```


```{r}
esquisser(viewer = "browser")
```
```{r}
ggThemeAssist(viewer= 'browser')
```



PLOT TOP 10 STATE BY DONATION

```{r}
state_donor$state <- factor(state_donor$state)%>%
  fct_reorder(state_donor$state_donation)

ggplot(state_donor) +
  aes(x = state, y = state_donation, fill = state) +
  geom_col() +
  scale_fill_manual(
    values = c(Ohio = "#A50026",
    Georgia = "#DA362A",
    Tennessee = "#F67B49",
    `District of Columbia` = "#FDBE6E",
    Illinois = "#FEEDA2",
    Virginia = "#E9F6A2",
    `New York` = "#B7E075",
    Florida = "#74C364",
    Texas = "#229C52",
    California = "#006837")
  ) +
  labs(title = "TOP 10 STATE BY DONATIONS", color = 'blue') +
  coord_flip() +
  theme(legend.position = "none")+
  theme_minimal()+
  geom_text(aes(label = signif(state_donation)), nudge_y = 1, color = 'blue', size = 2)


```



```{r}
 ggplot(donorinerj) +
  aes(
    x = donation_frequency,
    fill = gender,
    group = gender,
    weight = donations
  ) +
  geom_bar(position = "dodge") +
  scale_fill_manual(
    values = c(Female = "#8E0152",
    Male = "#276419")
  ) +
  labs(title = "DONATIONS BY GENDER/DONATION FREQUENCIES") +
  theme_minimal() +
  theme(plot.title = element_text(size = 10L, face = "bold"))
  #geom_text(aes(label = signif(count)), nudge_y = 1, color = 'blue', size = 2)

```




  
  
```{r}
gender =c('Female','Male')
total_donation=c(121457 ,127628)
pie(x=total_donation, labels = total_donation, radius = 1, col = c('pink','blue'))

```


  





```{r}
export(count_and_total_donation_jobfield, 'count_and_total_donation_jobfield_country.xlsx')


```











 
 